\plaintitle

### 2016-12-14 paper/proceedings.tex
node.js server initial setup with nginx reverse proxy

\begin{abstract}

Click to Sort

Interactive visualization is most powerful when it can provide different views of the data, empowering the user to explore the information from different angles.
d3.js textbook
  UPDATED---\today. This sample paper describes the formatting
  requirements for SIGCHI conference proceedings, and offers
  recommendations on writing for the worldwide SIGCHI
  readership. Please review this document even if you have submitted
  to SIGCHI conferences before, as some format details have changed
  relative to previous years. Abstracts should be about 150 words and
  are required.
\end{abstract}

@@

\section{Previous Work}
	Talbot et al. 2009 developed a visualization designed to support a particular task in machine learning: combining multi-class classifiers into ensembles of classifiers. An ensemble classifier is an aggregation of individually-weak classifier that in combination (through majority voting, or a weighted combination of class-membership probabilities) classifies an object into one of many possible classes. EnsembleMatrix uses a heat-map confusion matrix as its central visualization tool. A confusion matrix shows which classes are misclassified by visualizing them as a heatmap grid. The classes are given on the rows and columns. When a grid entry is dark, that means the class on the row has been classified as the class on the column. A perfect classifier would have a single dark line down the diagonal from left to right. EnsembleMatrix and provides two points of control for a user based on the confusion matrix: (1) a widget that controls the linear weighting of each classifier, and (2) a data-partitioning tool that splits the training data into subsets according to what class they belong to. Confusion matrices are visible for each of the classifiers separately, as well as an ensemble confusion matrix for all of them. (1) allows a user to upweight classifiers that perform well, and (2) allows a user to select subsets of the data to apply custom weighting schemes. Talbot et al. 2009 show that is users start  state-of-the-art classifiers, users are usually able to construct and ensemble at least as good as the state of the art, and sometimes better. This highlights the value that visualization tools can have for machine learning practitioners. In contrast to the present study, they use their visualization for a later stage in the machine learning pipeline, once a group of models has already been constructed.  The d3.js tool presented in this paper is used for an earlier stage: determining what model class and what features would be useful to explore.

>>>>

\begin{abstract}
  UPDATED---\today. This sample paper describes the formatting
  requirements for SIGCHI conference proceedings, and offers
  recommendations on writing for the worldwide SIGCHI
  readership. Please review this document even if you have submitted
  to SIGCHI conferences before, as some format details have changed
  relative to previous years. Abstracts should be about 150 words and
  are required.
\end{abstract}

@@

\section{Page Size and Columns}
On each page your material should fit within a rectangle of 7 $\times$
9.15 inches (18 $\times$ 23.2 cm), centered on a US Letter page (8.5
$\times$ 11 inches), beginning 0.85 inches (1.9 cm) from the top of
the page, with a 0.3 inches (0.85 cm) space between two 3.35 inches
(8.4 cm) columns. Right margins should be justified, not
ragged. Please be sure your document and PDF are US letter and not A4.
